    \documentclass[11pt,
        usenames, % allows access to some tikz colors
        dvipsnames % more colors: https://en.wikibooks.org/wiki/LaTeX/Colors
    ]{article}
    \usepackage{
        amsmath,
        amssymb,
        fouriernc, % fourier font w/ new century book
        fancyhdr, % page styling
        lastpage, % footer fanciness
        hyperref, % various links
        setspace, % line spacing
        amsthm, % newtheorem and proof environment
        mathtools, % \Aboxed for boxing inside aligns, among others
        float, % Allow [H] figure env alignment
        enumerate, % Allow custom enumerate numbering
        graphicx, % allow includegraphics with more filetypes
        wasysym, % \smiley!
        upgreek, % \upmu for \mum macro
        listings, % writing TrueType fonts and including code prettily
        tikz, % drawing things
        booktabs, % \bottomrule instead of hline apparently
        xcolor, % colored text
        cancel % can cancel things out!
    }
    \usepackage[margin=1in]{geometry} % page geometry
    \usepackage[
        labelfont=bf, % caption names are labeled in bold
        font=scriptsize % smaller font for captions
    ]{caption}
    \usepackage[font=scriptsize]{subcaption} % subfigures

    \newcommand*{\scinot}[2]{#1\times10^{#2}}
    \newcommand*{\dotp}[2]{\left<#1\,\middle|\,#2\right>}
    \newcommand*{\rd}[2]{\frac{\mathrm{d}#1}{\mathrm{d}#2}}
    \newcommand*{\pd}[2]{\frac{\partial#1}{\partial#2}}
    \newcommand*{\rdil}[2]{\mathrm{d}#1 / \mathrm{d}#2}
    \newcommand*{\pdil}[2]{\partial#1 / \partial#2}
    \newcommand*{\rtd}[2]{\frac{\mathrm{d}^2#1}{\mathrm{d}#2^2}}
    \newcommand*{\ptd}[2]{\frac{\partial^2 #1}{\partial#2^2}}
    \newcommand*{\md}[2]{\frac{\mathrm{D}#1}{\mathrm{D}#2}}
    \newcommand*{\pvec}[1]{\vec{#1}^{\,\prime}}
    \newcommand*{\svec}[1]{\vec{#1}\;\!}
    \newcommand*{\bm}[1]{\boldsymbol{\mathbf{#1}}}
    \newcommand*{\uv}[1]{\hat{\bm{#1}}}
    \newcommand*{\ang}[0]{\;\text{\AA}}
    \newcommand*{\mum}[0]{\;\upmu \mathrm{m}}
    \newcommand*{\at}[1]{\left.#1\right|}
    \newcommand*{\bra}[1]{\left<#1\right|}
    \newcommand*{\ket}[1]{\left|#1\right>}
    \newcommand*{\abs}[1]{\left|#1\right|}
    \newcommand*{\ev}[1]{\left\langle#1\right\rangle}
    \newcommand*{\p}[1]{\left(#1\right)}
    \newcommand*{\s}[1]{\left[#1\right]}
    \newcommand*{\z}[1]{\left\{#1\right\}}

    \newtheorem{theorem}{Theorem}[section]

    \let\Re\undefined
    \let\Im\undefined
    \DeclareMathOperator{\Res}{Res}
    \DeclareMathOperator{\Re}{Re}
    \DeclareMathOperator{\Im}{Im}
    \DeclareMathOperator{\Log}{Log}
    \DeclareMathOperator{\Arg}{Arg}
    \DeclareMathOperator{\Tr}{Tr}
    \DeclareMathOperator{\E}{E}
    \DeclareMathOperator{\Var}{Var}
    \DeclareMathOperator*{\argmin}{argmin}
    \DeclareMathOperator*{\argmax}{argmax}
    \DeclareMathOperator{\sgn}{sgn}
    \DeclareMathOperator{\diag}{diag\;}

    \colorlet{Corr}{red}

    % \everymath{\displaystyle} % biggify limits of inline sums and integrals
    \tikzstyle{circ} % usage: \node[circ, placement] (label) {text};
        = [draw, circle, fill=white, node distance=3cm, minimum height=2em]
    \definecolor{commentgreen}{rgb}{0,0.6,0}
    \lstset{
        basicstyle=\ttfamily\footnotesize,
        frame=single,
        numbers=left,
        showstringspaces=false,
        keywordstyle=\color{blue},
        stringstyle=\color{purple},
        commentstyle=\color{commentgreen},
        morecomment=[l][\color{magenta}]{\#}
    }

\begin{document}

\linespread{1.15}

\title{Octupole-order Lidov-Kozai Population Statistics}
\author{Yubo Su}
\date{Today}

\maketitle

\section{10/22/20---Initial Thoughts}

\subsection{Equations}

The equations of motion we want to study come from LML15. Describe the inner
binary by $\p{a, e, I, \ascnode, \omega}$ and the outer binary with ``out''
subscripts, and denote $I_{\rm tot} = I + I_{\rm out}$. Call the inner binary
component masses $m_1$, $m_2$, and the tertiary mass $m_3$, define the inner
binary total and reduced masses $m_{12} = m_1 + m_2$ and $\mu = m_1m_2 /
m_{12}$, and define the tertiary orbit total and reduced masses $m_{123} =
m_{12} + m_3$ and $\mu_{\rm out} = m_{12}m_3 / m_{123}$. The equations of motion
are ($j(e) = \sqrt{1 - e^2}$)
{\small
\begin{align}
    \rd{a}{t} ={}& -\frac{64}{5}\frac{a}{t_{\rm GW}j^7(e)}
            \p{1 + \frac{73}{24}e^2 +
            \frac{37}{96}e^4},
\end{align}
\begin{align}
    \rd{e}{t} ={}& \frac{j(e)}{64t_{\rm LK}}\Big\{
            120 e \sin^2 I_{\rm tot} \sin \p{2\omega}\nonumber\\
        &+ \frac{15 \epsilon_{\rm oct}}{8}\cos \omega_{\rm out}
            \big[\p{4 + 3e^2}\p{3 + 5\cos (2I_{\rm tot})}\nonumber\\
        &\times \sin \omega + 210 e^2\sin^2I_{\rm tot} \sin 3\omega\big]
            \nonumber\\
        &- \frac{15 \epsilon_{\rm oct}}{4} \cos I_{\rm tot} \cos \omega
            \big[15(2 + 5e^2) \cos \p{2I_{\rm tot}}\nonumber\\
        &+ 7\p{30 e^2 \cos(2\omega) \sin^2 I_{\rm tot} - 2 - 9e^2}]
                \sin \omega_{\rm out}\Big\}\nonumber\\
        &- \frac{304}{15}\frac{e}{t_{\rm GW}j^5(e)}
            \p{1 + \frac{121}{304}e^2},
\end{align}
\begin{align}
    \rd{I}{t} ={}& -\frac{3e}{32t_{\rm LK}j(e)}\Big\{
            10\sin\p{2I_{\rm tot}}\big[e \sin (2\omega)\nonumber\\
        &+ \frac{5\epsilon_{\rm oct}}{8}\p{2 + 5e^2 + 7e^2\cos(2\omega)}
            \cos \omega_{\rm out}\sin \omega\big]\nonumber\\
        &+ \frac{5\epsilon_{\rm oct}}{8} \cos \omega \big[
            26 + 37e^2 -35 e^2\cos(2\omega)\nonumber\\
        &- 15\cos\p{2I_{\rm tot}}\p{7e^2\cos (2\omega) - 2 - 5e^2}\big]\nonumber\\
        &\times \sin I_{\rm tot}\sin \omega_{\rm out}\Big\}
\end{align}
\begin{align}
    \rd{\ascnode}{t} ={}& \rd{\ascnode_{\rm out}}{t}
            = -\frac{3\csc I}{32 t_{\rm LK}j(e)}\Big\{
            2\big[(2 + 3e^2 - 5e^2 \cos (2\omega))\nonumber\\
        &+ \frac{25 \epsilon_{\rm oct}e}{8} \cos \omega
            \p{2 + 5e^2 - 7e^2\cos(2\omega)}\cos \omega_{\rm out}\big]\nonumber\\
        &\times\sin (2I_{\rm tot}) - \frac{5\epsilon_{\rm oct}e}{8}
            \big[35e^2(1 + 3\cos\p{2I_{\rm tot}})\cos 2\omega\nonumber\\
        &- 46 - 17e^2 - 15\p{6 + e_1^2}\cos\p{2I_{\rm tot}}\big]\nonumber\\
        &\times \sin I_{\rm tot} \sin \omega \sin \omega_{\rm out}\Big\},
\end{align}
\begin{align}
    \rd{\omega}{t} ={}& \frac{3}{8t_{\rm LK}}
            \Big\{\frac{1}{j(e)} \big[4 \cos^2 I_{\rm tot}
            + \p{5 \cos (2\omega) - 1}\nonumber\\
        &\times \p{1 - e^2 - \cos^2 I_{\rm tot}}\big] + \frac{L \cos I_{\rm tot}}{
            L_{\rm out}j(e_{\rm out})}\big[2 + e^2(3\nonumber\\
        &- 5\cos(2\omega))\big]\Big\}
        + \frac{15 \epsilon_{\rm oct}}{64t_{\rm LK}}\Big\{
            \p{\frac{L}{L_{\rm out}j(e_{\rm out})}
                + \frac{\cos I_{\rm tot}}{j(e)}}\nonumber\\
        &\times e\big[\sin \omega \sin \omega_{\rm out}
            \s{10(3\cos^2 I_{\rm tot} - 1)(1 - e^2) + A}\nonumber\\
        &- 5B\cos I_{\rm tot}\cos \Theta\big] - \frac{j(e)}{e}
            \big[10 \sin \omega \sin \omega_{\rm out}\cos I_{\rm tot}\nonumber\\
        &\times \sin^2 I_{\rm tot}\p{1 - 3e^2} + \cos \Theta\p{3A -
            10\cos^2 I_{\rm tot} + 2}\big]\Big\}\nonumber\\
        &+ \Omega_{\rm GR},
\end{align}
\begin{align}
    \rd{e_{\rm out}}{t} ={}& \frac{15eL\,j(e_{\rm out})\epsilon_{\rm oct}}{
            256t_{\rm LK}e_{\rm out}L_{\rm out}}\Big\{ \cos \omega
                \big[6 - 13e^2\nonumber\\
        &+ 5(2 + 5e^2)\cos (2I_{\rm tot}) + 70e^2 \cos (2\omega) \sin^2 I_{\rm
            tot}\big]\nonumber\\
        &\times \sin \omega_{\rm out} - \cos I_{\rm tot} \cos \omega_{\rm out}
            \big[5(6 + e^2)\cos \p{2I_{\rm tot}}\nonumber\\
        &+ 7\p{10e^2 \cos (2\omega) \sin^2 I_{\rm tot} - 2 + e^2}\big]
            \sin \omega\Big\},
\end{align}
\begin{align}
    \rd{I_{\rm out}}{t} ={}& -\frac{3eL}{32t_{\rm LK}j(e_{\rm out}) L_{\rm out}}
            \Big\{ 10\big[2e \sin I_{\rm tot} \sin (2\omega)\nonumber\\
        &+ \frac{5\epsilon_{\rm oct}}{8}\cos \omega\p{
            2 + 5e^2 - 7e^2\cos (2\omega)}\sin (2I_{\rm tot})\sin \omega_{\rm
            out}\big]\nonumber\\
        &+ \frac{5\epsilon_{\rm oct}}{8}\big[26 + 107e^2
            + 5(6 + e^2)\cos(2I_{\rm tot})\nonumber\\
        &- 35 e^2\p{\cos 2(I_{\rm tot}) - 5} \cos (2\omega)\big]
            \cos \omega_{\rm out}\sin I_{\rm tot} \sin \omega\Big\},
\end{align}
\begin{align}
    \rd{\omega_{\rm out}}{t} ={}&
        \frac{3}{16t_{\rm LK}}\Big\{\frac{2\cos I_{\rm tot}}{j(e)}
            \s{2 + e^2(3 - 5\cos(2\omega))}\nonumber\\
        &+ \frac{L}{L_{\rm out}j(e_{\rm out})}\big[4 + 6e^2
            + (5\cos^2 I_{\rm tot} - 3)\nonumber\\
        &\times [2 + e^2(3 - 5\cos(2\omega))]\big]\Big\}
            - \frac{15 \epsilon_{\rm oct}e}{64t_{\rm LK}e_{\rm out}}\nonumber\\
        &\times \Big\{ \sin \omega \sin \omega_{\rm out}\Big[
            \frac{L(4e_{\rm out}^2 + 1)}{e_{\rm out}L_{\rm out} j(e_{\rm out})}
            10 \cos I_{\rm tot}\sin^2 I_{\rm tot}\nonumber\\
        &\times(1 - e^2) - e_{\rm out}\p{\frac{1}{j(e)} +
            \frac{L \cos I_{\rm tot}}{L_{\rm out}j(e_{\rm out})}}\nonumber\\
        &\times\s{A + 10\p{3\cos^2 I_{\rm tot} - 1}\p{1 - e^2}}\Big]
            + \cos \Theta\nonumber\\
        &\times \Big[5B\cos I_{\rm tot}e_{\rm out}\p{\frac{1}{j(e)} +
            \frac{L \cos I_{\rm tot}}{L_{\rm out}j(e_{\rm out})}}\nonumber\\
        &+ \frac{L\p{4e_{\rm out}^2 + 1}}{e_{\rm out}L_{\rm out}j(e_{\rm out})}
            A\Big]\Big\}.
\end{align}
}
where $n = \sqrt{Gm_{12} / a^3}$ is the mean motion, $L = \mu \sqrt{Gm_{12}a}$
and $L_{\rm out} = \mu_{\rm out}\sqrt{Gm_{123}a_{\rm out}}$ are the circular
angular momenta, and
\begin{align}
    t_{\rm LK}^{-1} &= n\p{\frac{m_3}{m_{12}}}\p{\frac{a}{a_{\rm out}j(e_{\rm
        out})}}^3,\\
    t_{\rm GW}^{-1} &= \frac{G^3\mu m_{12}^2}{c^5a^4},\\
    \Omega_{\rm GR} &= \frac{3Gnm_{12}}{c^2aj^2(e)},\\
    \epsilon_{\rm oct} &= \frac{m_2 - m_1}{m_{12}}\frac{a}{a_{\rm out}}
        \frac{e_{\rm out}}{1 - e_{\rm out}^2},\\
    A &\equiv 4 + 3e^2 - \frac{5}{2}B\sin^2 I_{\rm tot},\\
    B &\equiv 2 + 5e^2 - 7e^2 \cos(2\omega),\\
    \cos \Theta &\equiv -\cos \omega \cos \omega_{\rm out}
        - \cos I_{\rm tot} \sin \omega \sin \omega_{\rm out}.
\end{align}

These equations can be nondimensionalized via the following steps (I won't
rewrite the equations): (i) multiply through by $t_{\rm LK, 0}$ ($a = a_0$ and
$e_{\rm out} = 0$), and call $\tau \equiv t / t_{\rm LK, 0}$ the new variable of
differentiation, (ii) re-express all of the timescales as
\begin{align}
    \frac{t_{\rm LK, 0}}{t_{\rm LK}} &= \p{\frac{a}{a_0}}^{3/2}
        j^{-3}\p{e_{\rm out}},\\
    \frac{t_{\rm LK, 0}}{t_{\rm GW}} &=
        \frac{G^3\mu m_{12}^3}{m_3c^5a^4}\frac{1}{n_0}\p{\frac{a_{\rm out}
            }{a_0}}^3,\nonumber\\
        &= \epsilon_{\rm GW}\p{\frac{a_0}{a}}^4,\\
    \epsilon_{\rm GW} &\equiv \frac{G^3\mu m_{12}^3
        a_{\rm out}^3}{m_3c^5a_0^7 n_0},\\
    \Omega_{\rm GR}t_{\rm LK, 0} &= \frac{3Gnm_{12}^2}{m_3c^2a}
        \frac{1}{n_0}\p{\frac{a_{\rm out}}{a_0}}^3,\nonumber\\
        &= \epsilon_{\rm GR} \p{\frac{a_0}{a}}^{5/2},\\
    \epsilon_{\rm GR} &= \frac{3Gm_{12}^2a_{\rm out}^3}{m_3c^2a_0^4}.
\end{align}
(iii) re-express $\rdil{a}{t}$ as
\begin{equation}
    \rd{(a / a_0)}{\tau} = -\frac{64}{5}\frac{\epsilon_{\rm GW}}{
        j^{7/2}(e)}\p{\frac{a_0}{a}}^3\p{1 + \frac{73}{24}e^2 +
        \frac{37}{96}e^4}.
\end{equation}
As such, the natural unit of length is $a_0 = 1$, the natural unit of time is
$t_{\rm LK, 0} = 1$, and everything else is dimensionless. When computing these
$\epsilon$, I use convention where $1 M_{\odot} = 1\;\mathrm{AU} = c = 1$, under
which $G = 9.87 \times 10^{-9}$.

\subsection{Points of Inquiry}

The goal is to understand how the merger window varies as a function of $q
\equiv m_1 / m_2$ ($m_1 < m_2$) when the octupole order LK effects are
important.
\begin{itemize}
    \item First, let's set $\epsilon_{\rm GW} = 0$. It is well known that the
        octupole order LK is nonintegrable. What does the Fourier spectrum of
        the eccentricity look like? Will this help us get a delay time
        distribution between high-e phases?

        When the octupole effect is unimportant, the spectrum falls off
        exponentially over scales $\tau \simeq P_{\rm LK} j^{-1}(e_{\max})$,
        where $P_{\rm LK}$ is the quadrupole LK period. One imagines the
        tail of the spectrum gets heavier when $\epsilon_{\rm oct}$ is
        increased, and this might help us get the delay time distribution.

        A second way we can postprocess this is to take a histogram of $e(t)$.
        If there is some regular structure, it's likely this will allow us to
        compute the average rate of binary coalescence due to GW radiation.

    \item The goal is to understand the size of the merger window, $\Delta I$,
        as a function of $q$. To do this, we numerically sample the merger time
        function $T_{\rm m}\p{I_0, q}$. At each $I_0$, the natural thing to do
        would be to try for $\sim 5-10$ random $\Omega, \omega$, and define the
        merger window to be where $T_{\rm m} \leq 10^10\;\mathrm{yr}$.
\end{itemize}

\section{11/02/20}

We've done a lot more inquiry on this, read the Nov 3 weekly for a recap. In
summary though, there should roughly be two ways to have LK-induced mergers:
\begin{itemize}
    \item Quadrupole LK-induced mergers. The $e_{\max}$ of these systems is well
        understood, however, and the merger fraction should be easy to
        calculate: we can get the merger time using the $T_m \propto \p{1 -
        e_{\max}}^{-3}$ physically-justified fitting law from LL18 in the
        LK-induced regime, and we just have to evaluate where it crosses
        $10\;\mathrm{Gyr}$.

    \item Octupole LK-induced mergers. For these, there is a characteristic
        initial inclination range for which orbit flipping occurs, which is a
        function of $\epsilon_{\rm oct}$. This can likely be calculated
        analytically, but I'm not sure yet.

        For these systems, there is a characteristic orbit flipping timescale
        that is robust up to a factor of a few (since $K$ oscillates on a fixed
        timescale, and orbit flips occur whenever $K$ crosses $-\eta/2$), call
        this $t_{\rm ELK}$. Thus, octupole LK-induced mergers occur over
        characteristic times $t_{\rm ELK}$ within the desired inclination window
        (as once the system reaches an orbit flipping eccentricity, it executes
        a one-shot merger, approximately). It is well known that $t_{\rm ELK}$
        depends on $\epsilon_{\rm oct}$, see e.g.\ Antognini 2015.

        There is some small variability, however, in this picture, according to
        my plots. This can likely be attributed to the exact history of
        eccentricity maxima prior to the one-shot maximum, since particularly
        dissipative sequences (i.e.\ many large eccentricity maxima prior to
        undergoing ``the big one'') can shrink the orbit and change the LK cycle
        pattern.
\end{itemize}

Armed with this, we should have enough information to compute the indicator
function $\mathbb{I}_{\rm merge}\p{a_{\rm in}, I_0, t_{\rm LK}, \epsilon_{\rm
oct}}$, whether a system will merge, by simply computing the two ranges of $I_0$
from above. This should be valid wherever we are in a strongly LK-induced
regime, i.e.\ very large eccentricities are necessary to merge.

In fact, there's a possibility the critical $\epsilon_{\rm oct}$ can be
calculated analytically, see Katz et.\ al.\ 2011 for the test particle case. Is
this generalizable?

\subsection{The Quadrupole Conserved Quantity}

This is a quick derivation. To quadrupolar order, $L_{\rm out}$ is conserved, as
is the total angular momentum, so
\begin{align}
    L_{\rm tot}^2 &= L_{\rm out}^2 + L_{\rm in}^2 + 2L_{\rm out}L_{\rm in}
            \cos I,\\
    \frac{L_{\rm tot}^2 - L_{\rm out}^2}{L_{\rm out}L_{\rm in, 0}} &=
        \eta j_{\rm in}^2 + 2j_{\rm in}\cos I,\\
    \frac{1}{2}\s{\frac{L_{\rm tot}^2 - L_{\rm out}^2}{L_{\rm out}L_{\rm in, 0}}
        - \eta} &= j_{\rm in}\cos I - \eta \frac{e_{\rm in}^2}{2}.
\end{align}
This is the form of the constant given in LL18. Note that $\eta = \eta_0 /
j_{\rm out}$, where $\eta_0$ is evaluated at $e_{\rm out} = 0$ as well.

\section{11/03/20}

We found out that the critical inclination window has a clean fitting formula in
the test particle limit, MLL16 (which agrees with the leading order expansion of
Katz et al 2011). If we take $\epsilon_{\rm oct}$ to be small, then
\begin{align}
    \cos^2 I_0 &\leq \frac{\epsilon_{\rm oct}}{0.4},\\
    \Delta I_0 &\leq \sqrt{\frac{\epsilon_{\rm oct}}{0.4}}.
\end{align}
This marks the inclination window in which the octupole-order effects are
expected to be dominant, if the inclination window is similar to the test
particle case (it's not exactly, since with finite $\eta$ the window is offset
to larger $I_0$ than $I_{0, \lim}$)

We will make two simplifying assumptions:
\begin{itemize}
    \item DA is valid.
    \item $e_{\lim}$ is sufficiently large that one-shot mergers occur.
\end{itemize}
If we assume that DA is valid, then
\begin{align}
    t_{\rm LK}\sqrt{1 - e_{\max}^2} &\gtrsim \frac{1}{n_{\rm out}},\\
    \frac{a^{3/2}}{a_{\rm out}^{3/2}}\frac{m_{12}}{m_3}
        \p{\frac{a_{\rm out}}{a}}^{3}\sqrt{1 - e_{\max}^2}
            \p{1 - e_{\rm out}^2}^{3/2} &\gtrsim 1,\\
    \frac{a_{\rm out}}{a} &\gtrsim \frac{1}{j_{\min}^{2/3}}.
\end{align}
In the last line, we take $e_{\rm out} \sim 0.6$ for which $\p{1 - e_{\rm
out}^2}^{3/2} = 0.5$, and $m_{12} / m_3 = 2$. For some reference $e_{\max} =
10^{-4}$, $j_{\min}^{2/3} = 0.058$ (it's okay for DA to break down at
$e_{\lim}$, since one shot mergers should occur). TODO this should probably be
evaluated for $e_{\max}$ near the edge of the quadrupole merger window.

Recall also that
\begin{equation}
    \epsilon_{\rm oct} = \frac{1 - q}{1 + q}\frac{a}{a_{\rm out}}
        \frac{e_{\rm out}}{1 - e_{\rm out}^2}.
\end{equation}
Thus, in the DA regime, we can explicitly write down the merger window for
ELK-induced mergers
\begin{equation}
    f_{\rm oct} \equiv \frac{2\Delta I_0}{\pi}
        \lesssim \sqrt{\frac{1 - q}{1 + q}\frac{1}{2}\frac{e_{\rm out}}{1 -
            e_{\rm out}^2}}.
\end{equation}
This isn't great, since my data suggest that $\Delta I_0$ should be linear in
$(1-q)/(1+q)$, where $\epsilon_{\rm oct} \simeq 0.01$ should be small enough to
satisfy the assumptions. Bin's data also agree with this, at least up to $e_{\rm
out} = 0.6$ ($25^\circ$, $15^\circ$, $10^\circ$ degree merger windows for $q =
0.2$, $0.4$, $0.6$ respectively).

So it's clear that the ELK-active window should be revised for the finite-$\eta$
case.

\subsection{Differentiating $K$}

We showed earlier that the quadrupole-conserved quantity is
\begin{equation}
    K = j \cos I + j^2\eta = \frac{1}{2}\frac{L_{\rm tot}^2 - L_{\rm out}^2}{
        L_{\rm out}L_{\rm in, 0}}.
\end{equation}
Differentiating the second expression, we obtain that
\begin{align}
    \rd{K}{t} &= \frac{1}{2L_{\rm in, 0}}
        \p{\frac{-L_{\rm tot}^2}{L_{\rm out}^2} \rd{L_{\rm out}}{t}
            - \rd{L_{\rm out}}{t}},\\
        &= -\frac{1 + L_{\rm tot}^2 / L_{\rm out}^2}{2L_{\rm in, 0}}
            \uv{L}_{\rm out} \cdot \rd{\bm{L}_{\rm out}}{t}.
\end{align}
Indeed, from LML15, we see that this term vanishes to quadrupolar order, and
that the only terms that survive are (I use $1$ for in and $2$ for out somewhat
interchangeably, due to the source materials I'm pulling from)
\begin{align}
    \frac{\uv{L}_{\rm out}}{L_{\rm in}} \cdot \rd{\bm{L}_{\rm out}}{t}
        &= -\frac{75\epsilon_{\rm oct}}{64}\s{
            2\p{\bm{e}_1 \cdot \uv{n}_2}\p{\bm{j}_1 \cdot \uv{n}_2}
                \uv{L}_2 \cdot \p{\uv{u}_2 \times \bm{j}_1}
            + \s{\frac{8}{5}e_1^2 - \frac{1}{5}
                - 7\p{\bm{e}_1 \cdot \uv{n}_2}^2
                + \p{\bm{j}_1 \cdot \uv{n}_2}^2}
                \uv{L}_2 \cdot \p{\uv{u}_2 \times \bm{e}_1}
            }.
\end{align}
Triple products let us simplify a little bit to be in terms of $\uv{v}_2 =
\uv{L}_2 \times \uv{e}_2$ as in LML15. But this won't be useful: if we don't
have the second derivative as well, we can't compute a characteristic
oscillation frequency.

We can make one more approximation though: all of the $\bm{j}_1 \cdot \uv{n}_2$
terms are generally small, since they are of order $j_{1z}$ which is not
conserved exactly but remains small (this is similar to Katz's approximation).
This means we're left with
\begin{align}
    \rd{K}{t}
        &\approx \p{1 + \frac{\eta^2}{4}}
        \frac{75\epsilon_{\rm oct}}{64}
            \s{\frac{8}{5}e_1^2 - \frac{1}{5}
                - 7\p{\bm{e}_1 \cdot \uv{n}_2}^2}
                \bm{e}_1 \cdot \uv{v}_2.
\end{align}
We've assumed $L_{\rm tot}^2 / L_{\rm out}^2 \sim 1 + \eta^2/2$, since typically
$\bm{L}_{\rm in}$ and $\bm{L}_{\rm out}$ are misaligned by $I \simeq 90^\circ$.
This is again in agreement with the Katz formula except now $\bm{n}_2$ and
$\bm{v}_2$ are permitted to vary (and our prefactor).

Now, their $\Omega_{\rm e}$ is such that $e_z / e = \cos \Omega_{\rm e}$. This
is a bit more difficult to generalize for us, but it shouldn't be impossible. We
will return later if it proves interesting.

\subsection{Timescale Analysis}

Let's suppose we only consider systems with $T_{\rm m, 0} > 10\;\mathrm{Gyr}$,
that cannot merge in a Hubble time. For simplicity, we also require DA hold, and
all three masses be comparable ($m_{12} = 2m_3$, say). Then this places
constraint
\begin{equation}
    \frac{5c^5a_0^4}{256G^3m_{12}^2\mu} > 10\;\mathrm{Gyr}.
\end{equation}
If we fix $m_3 = 30M_{\odot}$, so $m_{12}^2\mu = q / (1+q)^2\p{30M_{\odot}}^3$,
then
\begin{equation}
    \frac{a_0}{0.202\;\mathrm{AU}}\p{\frac{2(1 + q)^2}{q}}^{1/4} > 1.
\end{equation}
This is a very weak constraint.

Nevertheless, if we are firmly in the LK-induced regime, LL18 can be used to
easily compute the quadrupole merger window, $I_{\rm 0, merger}^+ - I_{\rm 0,
merger}^-$ by just using their Eq.~(42) to compute $e_{\max}$. We know that in
the LK-induced regime, $\epsilon_{\rm GR}$ is very weak except for at very large
$e_{\max}$, so we can likely omit it when computing the $I_{\rm 0,
merger}^{\pm}$ since these are very smooth mergers. Then, since $j_{\min}^6 =
10\;\mathrm{Gyr} / T_{\rm m, 0}$, we can obtain
\begin{align}
    \cos I_{\rm 0, merger}^- - \cos I_{\rm 0, merger}^+
        &= \frac{1}{5}\sqrt{
            \p{5\eta - 4\eta j_{\min}^2}^2
            - 20\p{\frac{5\eta^2}{4}
                - j_{\min}^2\p{3 + \frac{9\eta^2}{4}}
                + \eta^2j_{\min}^4}},\\
        &\approx \frac{j_{\min}\sqrt{60}}{5}
            + \mathcal{O}\p{\eta j_{\min}},\\
        &\approx \frac{\sqrt{60}}{5}\p{\frac{10\;\mathrm{Gyr}}{T_{m, 0}}}^{1/6}
            + \mathcal{O}\p{\eta j_{\min}},\\
        &\approx \frac{\sqrt{60}}{5}\p{\frac{0.202\;\mathrm{AU}}{a_0}}^{2/3}
            \p{\frac{q}{2(1+q)^2}}^{1/6}
            + \mathcal{O}\p{\eta j_{\min}}.
\end{align}
For $I_{\rm 0, merger} \sim 90^\circ$, we can replace $\cos(x) \approx 90^\circ
- x$, and so the difference of these cosines is just the negative difference of
their arguments. For $q = 2/3$ and $a_0 = 100\;\mathrm{AU}$, this gives $\Delta
I_{\rm 0, merger} = 0.996^\circ$, while LL18 obtain $1.20^\circ$. Thus, this
seems to be the right scaling, and something more accurate can prboably be
obtained by using a more accurate $e_{\max}$.

\subsection{Origin of Probabilistic Wings}

I had a guess that may the origin of the probabilistic wings would be due to
separatrix breaking due to $\epsilon_{\rm oct}$, where the IC would either be
circulating or librating depending on $\omega_{\rm in}$. However, running some
data, this does not appear to be the case (\lstinline{emax_omega_sweep}), since
the distribution of emaxes between small and large values changes as a function
of time. This suggests that there is some characteristic timescale over which
systems in this intermediate probabilistic zone (where $I_0$ gives a probability
of merging within $10\;\mathrm{Gyr}$) encounter ELK-induced orbit flips. This is
not very surprising: it seems like $K$ basically oscillates sinusoidally (the
origin of the criterion I am thinking about above, for whether orbits can flip)
and has some small extra bit of wander. Maybe the degree of wander can be
quantified, in which case the behavior of these small probabilistic transition
zones can be understood.

\section{11/04/20}

We mentioned that when changing $q$ that the quadrupole strength. This could
have entailed holding $t_{\rm LK}$, $\epsilon_{\rm GR}$, $\epsilon_{\rm GW}$,
and $\eta$ constant, where
\begin{align}
    t_{\rm LK} &= \frac{1}{n_{\rm in}}\frac{m_{12}}{m_3}\p{\frac{a_{\rm out}\sqrt{1 -
        e_{\rm out}^2}}{a_{\rm in}}}^3,\\
    \eta &= \frac{\mu}{\mu_{\rm out}} \sqrt{\frac{m_{12}a_{\rm in}}{
        m_{123}a_{\rm out}\p{1 - e_{\rm out}^2}}},\\
    \epsilon_{\rm GR} &= \frac{3Gm_{12}^2a_{\rm out}^3}{m_3c^2a_0^4},\\
    \epsilon_{\rm GW} &\equiv \frac{G^3\mu m_{12}^3
        a_{\rm out}^3}{m_3c^5a_0^7 n_{\rm in}}.
\end{align}
However, this is a bit contrived. Instead, we will just vary $q$ with everything
fixed, and also consider varying $e_{\rm out}$ such that $t_{\rm LK}$ remains
fixed. We also should think about
\begin{align}
    \epsilon_{\rm oct} &= \frac{1 - q}{1 + q}\frac{a}{a_{\rm out}}
        \frac{e_{\rm out}}{1 - e_{\rm out}^2},\\
        &= \frac{1 - q}{1 + q}\frac{a}{a_{\rm out, eff}}
        \frac{e_{\rm out}}{\sqrt{1 - e_{\rm out}^2}}
\end{align}
where $a_{\rm out, eff} \equiv a_{\rm out}\sqrt{1 - e_{\rm out}^2}$.

So the goal will be to continue running with all my current $q \in [0.2, 0.3,
0.4, 0.5, 0.7, 1.0]$, but also give some different $e_{\rm out}$ while holding
$a_{\rm out, eff}$ constant. Let's try $e_{\rm out} = [0.6, 0.8, 0.9]$. Since
used $a_{\rm out} = 4500\;\mathrm{AU}$ for $e_{\rm out} = 0.6$, we will stick to
$a_{\rm out, eff} = 3600\;\mathrm{AU}$, the corresponding $a_{\rm out}$ that we
need are $a_{\rm out} = [4500, 6000, 8259]\;\mathrm{AU}$. This corresponds to
increasing $e_{\rm out}$ by roughly $3\times$.

\section{11/08/20}

While the above simulations are running, we observe three new ideas:
\begin{itemize}
    \item Notice that, for most parameters, if $e_{\rm in}$ can attain the
        critical value $e_{\lim}$ in the absence of GW, mergers occur when GW
        is turned on. This can be quantitatively evaluated, the one-shot merger
        eccentricity $e_{\rm os}$. Consider the scaling
        \begin{align}
            \rd{\ln a}{t} &= -\frac{64}{5j^7(e)}\p{1 + \frac{73}{24}e^2 +
                \frac{37}{96}e^4}\frac{G^3 \mu m_{12}^2}{c^5a^4},\\
                &\sim -j\p{e_{\max}}\frac{64}{5j^7(e_{\max})}
                    \frac{421}{96} \frac{G^3\mu m_{12}^2}{c^5a^4}.
        \end{align}
        We then seek where $\rdil{\ln a}{t} \sim -1 / t_{\rm LK}$, giving
        \begin{align}
            j^6\p{e_{\rm os}} \equiv j_{\rm os}
                &= \frac{842}{15}\frac{G^3 \mu m_{12}^2}{c^5a^4}
                    \frac{1}{n}\frac{m_{12}}{m_3}\p{\frac{a_{\rm out,
                    eff}}{a}}^3,\\
                &= \frac{842}{15}\frac{G^3 \mu m_{12}^3}{m_3c^5a^4n}
                    \p{\frac{a_{\rm out, eff}}{a}}^3.
        \end{align}
        Recall that $n = \sqrt{Gm_{12} / a^3}$.

        Then if $j_{\lim} \lesssim j_{\rm os}$ (i.e.\ $e_{\max} > e_{\rm os}$),
        then one shot mergers occur. We can derive a scaling relation
        \begin{align}
            0 &= \frac{3}{8}\p{j_{\lim}^2 - 1}\p{-3 + \frac{\eta^2}{4}
                \p{\frac{4}{5}j_{\lim}^2 - 1}} + \epsilon_{\rm GR}
                    \p{1 - 1/j_{\lim}},\\
            j_{\lim} &\approx \frac{8\epsilon_{\rm GR}}{9 + 3\eta^2/4}.
        \end{align}
        This holds when $\epsilon_{\rm GR}, j_{\lim} \ll 1$. Matching the two
        expressions, we obtain the criterion for one shot mergers occuring at
        $e_{\lim}$:
        \begin{align}
            842 \frac{G^{5/2}a_{\rm out, eff}^3 m_{12}^{5/2}\mu}{
                15a^{11/2}c^5 m_3}
                &\gtrsim \p{\frac{8}{9 + 3\eta^2/4}
                    \frac{3Gm_{12}^2a_{\rm out, eff}^3}{c^2a^4m_3}}^6,\\
            a^{37/2} &\gtrsim \frac{2^{18} \cdot 15}{842} \frac{G^{7/2}a_{\rm
                out, eff}^{15} m_{12}^{19/2}}{c^7 m_3^5 \mu \p{3 + \eta^2/4}^6}
                ,\\
            \p{\frac{a}{a_{\rm out, eff}}} &\gtrsim
                0.0118
                \p{\frac{a_{\rm out, eff}}{3600\;\mathrm{AU}}}^{-7/37}
                \p{\frac{m_{12}}{50M_{\odot}}}^{17/37}
                \p{\frac{30M_{\odot}}{m_3}}^{10/37}
                \p{\frac{q / (1 + q)^2}{1/4}}^{-2/37}.
        \end{align}
        where we have taken $q = 1$. In practice, we need a marginally smaller
        $a$ than this, since in the one-shot merger regime, GW has to strongly
        modify the trajectory near $e_{\max}$. Note that both my parameters ($a
        = 100\;\mathrm{AU}$, $a_{\rm out, eff} = 3600\;\mathrm{AU}$) and Bin's
        ($a = 10\;\mathrm{AU}$, $a_{\rm out, eff} = 300\;\mathrm{AU}$) roughly
        satisfy this.

    \item The above addresses the case of ELK-induced mergers, effectively
        ($e_{\lim}$ induced by ELK). Instead, we can consider the case of
        ELK-\emph{enhanced} mergers, in analogy with the quadrupole case. Here,
        quadrupole LK cannot merge the system alone, but with eccentricity
        cycles, the system is still able to merge. We can quantify this by
        computing an effective eccentricity over ELK-induced cycles:
        \begin{align}
            \ev{\rd{\ln a}{t}} &= -\ev{\frac{a}{t_{\rm GW}}},\\
                &\approx -\frac{a}{t_{\rm GW, 0}}
                    \ev{\frac{1 + 73e_{\max}^2/24 + 37e_{\max}^4/96}
                        {j^6(e_{\max})}},\\
                &\equiv -\frac{a}{t_{\rm GW,0}}
                    \underbrace{\p{\frac{1 + 73e_{\rm eff}^2/24 + 37e_{\rm
                    eff}^4/96}{j^6(e_{\rm eff})}}}_{f\p{e_{\rm eff}}}.
        \end{align}
        where the average is taken over many LK cycles, and $t_{\rm GW, 0}$
        denotes the $e = 0$ evaluation.

        We can then ask what level of $e_{\rm eff}$ is required to induce
        merger within a Hubble time $t_{\rm Hubb}$. This can also be estimated
        \begin{align}
            \frac{t_{\rm GW, 0}}{t_{\rm Hubb}}\frac{1}{f\p{e_{\rm eff}}}
                &\lesssim 1,\\
            \p{\frac{4t_{\rm Hubb}}{t_{\rm GW, 0}}}^{1/6}
                &\gtrsim j\p{e_{\rm eff}},\\
            0.01461\p{\frac{100\;\mathrm{AU}}{a}}^{2/3} &\gtrsim
                j\p{e_{\rm eff}},\\
            1 - e_{\rm eff} &\lesssim 1.068 \times 10^{-4}.
        \end{align}

    \item Finally, we notice in the data that the zone of ELK excitation seems
        to exhibit a gap near $I_0 \approx 90^\circ$, unlike in the test mass
        limit, for which ELK is symmetric about $I_0 = 90^\circ$. We can
        understand this: the ELK-induced eccentricity oscillations in the
        massless limit occur due to ELK-induced oscillations in the
        quadrupole-conserved quantity $j_z = j\cos I$.

        When $\eta > 0$, the conserved quantity is instead $j\cos I + \eta j^2$
        (LL18, or earlier in notes). Thus, we can understand that if $I_0$ is
        such that $j\cos I \lesssim \eta j^2$, that $\eta$ suppresses ELK
        oscillations. This can be solved to estimate the range over which the
        conserved quantity is dominated by the $\eta$ contribution:
        \begin{equation}
            \abs{\cos I} \lesssim \eta.
        \end{equation}
        Within this range, we expect any oscillations in $j$ to be suppressed.

        NB\@: I don't think $j \cos I + \eta j^2$ is the ``generalization'' of
        $j_z$, since it is the $z$ component of the total angular momentum.
        Instead, the generalization should be something like $-j\cos I + \eta
        j^2$, i.e.\ the $z$ component of $\bm{L}_{\rm out} - \bm{L}_{\rm in}$,
        which is only conserved when $\eta \to 0$.
\end{itemize}

With the above, it seems we should be able to characterize what shapes the
$T_{\rm m}$ behavior:
\begin{itemize}
    \item In the very center, near $I_{\lim}$, we have a quadrupole merger
        window.

    \item At the very edge of the quadrupole merger window (towards $I >
        90^\circ$, as the other direction is $\eta$-suppressed), we have some
        small ELK enhancement of the merger rate due to eccentricity
        oscillations.

    \item Farther away from the quadrupole merger window, there are ELK-induced
        orbit flips, which merger since $e_{\lim} < e_{\rm os}$.

    \item On the boundaries of the ELK orbit flipping region, there are some
        other ELK-enhanced mergers. This region is generally probabilistic,
        where the $e_{\max}$ distribution is bimodal. This is expected to be
        wider for smaller $a$, as a result.
\end{itemize}

\section{11/15/20}

We have a new idea. While the system is nonintegrable, it can only explore a
bounded area of phase space, according to our simulations. We try to obtain a
bound using the Hamiltonian. Consider the full Hamiltonian, which is $H\p{e_1,
\omega_1, I_1, e_2, \omega_2, I_2}$. We omit the $\Omega$ dependencies since we
are just evaluating it as a constant of motion, not trying to get EOMs. There
are two primary simplifications:
\begin{itemize}
    \item By the law of sines, $L_1 \sin I_1 = L_2 \sin I_2$, where $L_1 =
        \mu\sqrt{Gm_{12}a_{\rm in}(1 - e_1^2)}$ and for $L_2$.

    \item By conservation of total angular momentum:
        \begin{equation}
            \frac{L_{\rm tot}^2}{L_{\rm out, 0}^2}
                = j_{\rm out}^2 + \eta_0^2 j_{\rm in}^2
                    + 2j_{\rm in} j_{\rm out} \eta_0 \cos I_{\rm tot},
        \end{equation}
        where $\eta_0 = L_{1,0} / L_{2,0}$ is the angular momentum ratio at zero
        eccentricity.
\end{itemize}
Putting together these two constraints, these implicitly give $(e_2, I_2)$ as a
function of $\p{e_1, I_1, \eta_0, L_{\rm tot, i}}$, the initial total angular
momentum. Thus, the Hamiltonian is reduced to $H\p{e_1, \omega_1, I_1,
\omega_2}$. Of these, the quadrupole term does not depend on $\omega_2$, so we
see that to obtain the Hamiltonian of the entire system to quadrupolar order, we
only need to specify $e_1, \omega_1, I_1$. This already hints that oscillations
in $e_2$ are bounded, and that indeed for systems sufficiently far from
$I_{\lim}$, they cannot be driven to $I_{\lim}$ by octupole-induced DA
oscillations.

To understand whether a system can be driven to flip orbits, we assume that
$H_{\rm quad}$ evolves non-integrably within some bound region, and we wish to
understand whether the bound region contains $H_{\lim} \equiv H_{\rm quad}\p{0,
0, I_{\lim}}$. Indeed, if octupole-order effects act slowly, within each orbit,
the system should execute an approximately quadrupolar oscillation, so the only
way it will reach $e_{\lim}$ is if it starts from $I_{\lim}$ (this is accurate
so long as the $\epsilon_{\rm GR}$-induced flatness in the $e_{\max}$ curve can
be neglected; maybe we can incorporate the $\Phi_{\rm GR}$ into the Hamiltonian?
unlikely).

A simple criterion exists to compare the two. We assume that $H_{\rm quad}$
evolves randomly within an interval of magnitude $H_{\rm oct}$. By inspection,
we can read off the values for which $H_{\rm oct}$ is maximized/minimized:
\begin{align}
    H_{\rm oct} &\propto e_1 e_2 \p{
        A \cos \phi + 10 \cos I_{\rm tot} \sin^2 I_{\rm tot} j_1^2
        \sin \omega_1 \sin \omega_2},\\
    A &= 4 + 3e_1^{2} - \frac{5(2 + 5e_1^2 - 7e_1^2 \cos 2\omega_1)}{2}
        \sin I_{\rm tot},\\
    \cos \phi &= -\cos \omega_1 \cos \omega_2 - \cos I_{\rm tot} \sin \omega_1
        \sin \omega_2.
\end{align}
Let's assume $e_2 = e_{2, 0}$ for simplicity, accurate to leading order. We can
then bound $H_{\rm oct}$ by numerically solving. This proves to be quite
good at reproducing the MLL16 fitting formula, I think (to be checked
quantitatively)!

\section{11/15/20}

A clear problem arises though. When we are trying to reach $I_{\lim} = 90^\circ$
like in the TP limit, everything is fine. However, when $\eta > 0$, $I_{\lim} >
90^\circ$. To leading order, everything makes sense: an ELK-active region
expands about $I_{\lim}$, and we can probably predict this (TODO try).

However, a conundrum arises: $H$ is symmetric in $I$. If $\abs{H_{\rm oct}}$ is
large enough, everything within a zone centered on $90^\circ$ should be able to
access $I_{\lim}$. What is the origin of the gapped region then?

My current hypothesis is that this has to do with the actual amplitude of
oscillations in $K$ (returning to an early plot I made). Katz11 shows that
$\rdil{K}{t} \propto -K$ roughly, so it's likely that $K$ cannot reach
$K(I_{\lim})$ when it starts too near zero. This still doesn't explain why the
ELK window itself is asymmetric though. It's surprising this becomes
insufficient when $\eta > 0$.

For today/tomorrow, our goal will just be to show that this reproduces the
correct formula in the TP limit, then we will also make a plot of $\Delta K(I)$
in the nonzero-$\eta$ case, and use this to support our notion of a ``gap.'' I
don't think I can come up with anything quantitative, especially since I've
basically only had the weekend to think about this.

Edit (11/17/20): I made a plot of the $\Delta K(I)$ plot and it turned out
exactly as expected. It remains to be seen whether an obvious analytical bound
can be written down, but it may not be necessary for the purposes of this paper.

\section{01/15/21}

I've been mostly just writing up notes, I gave up on an analytical expression.

Our notation in the paper is that $P_{\rm merge}$ is the merger probability, for
a given $I_0$, $q$, and $e_{\rm out}$. Then
\begin{equation}
    f_{\rm merge}(q, e_{\rm out}) \propto
        \int\limits_{-1}^1 P_{\rm merge}(I_0, q, e_{\rm out})\;\mathrm{d}\cos
        I_0.
\end{equation}
We also use the notation
\begin{equation}
    f_{\rm merge}(q) \propto \int\limits_0^{0.9}\int\limits_{-1}^1 P_{\rm merge}(I_0,
        q, e_{\rm out}) P(e_{\rm out}) \;\mathrm{d}\cos I_0\;\mathrm{d}e_{\rm
        out}.
\end{equation}
We are also motivated to investigate because
\begin{equation}
    \rd{\ln a}{t} \propto \mu = \frac{q}{(1 + q)^2}.
\end{equation}
where
\begin{equation}
    q \equiv m_2 / m_1.
\end{equation}

\section{02/15/21---Analytic $q$ distribution}

I've procrastinated on further work on this paper, since it's almost done, but
we add a brief blurb here. Consider if the primordial distribution of masses
follows a power law $P(m) \propto m^{-p}$ over some $m_{\min}$ and
$m_{\max}$; what is the distribution of $q$ when two stars are drawn from this
distribution? Moe \& di Stephano, in some of their papers, point out that $P(q)
\propto q^{-p}$, but I didn't see a derivation. We give one below.

WLOG, assume $m_2 \leq m_1$, then
\begin{align}
    P(m) &\propto m^{-p},\\
         &= \frac{m^{-p}}{N},\\
    N &= \frac{1}{p - 1}\p{m_{\min}^{1 - p} - m_{\max}^{1 - p}},\\
    P(q) &= \int\limits_{m_{\min}}^{m_{\max}}\int\limits_{m_{\min}}^{m_1}
            \delta\p{\frac{m_2}{m_1} - q}P(m_1) P(m_2)
            \;\mathrm{d}m_2\;\mathrm{d}m_1,\\
        &= \int\limits_{m_{\min}}^{m_{\max}} m_1 P(m_1) P(qm_1)
            \;\mathrm{d}m_1,\\
        &= \frac{p - 1}{m_{\min}^{1 - p} - m_{\max}^{1 - p}}
            \int\limits_{m_{\min}}^{m_{\max}}
            m_1
            \frac{p - 1}{m_{\min}^{1 - p} - m_1^{1 - p}}
            \p{m_1}^{-p}\p{qm_1}^{-p}\;\mathrm{d}m_1,\\
        &= q^{-p}\frac{(p - 1)^2}{m_{\min}^{1 - p} - m_{\max}^{1 - p}}
            \int\limits_{m_{\min}}^{m_{\max}}
            \frac{m_1^{-2p + 1}}{m_{\min}^{1 - p} - m_1^{1 - p}}
            \;\mathrm{d}m_1.
\end{align}
Here, $q_{\min} \equiv m_{\min} / m_{\max}$. The case where $m_2 \geq m_1$
equates to flipping the masses, so $P(q)$ is unaffected, and $P(q) \propto
q^{-p}$. In fact, by normalization, we find that
\begin{equation}
    P(q) = \frac{p - 1}{q_{\min}^{1 - p} - 1}q^{-p},
\end{equation}
where $q_{\min} = m_{\min} / m_{\max}$. These two expressions probably agree?
Not sure

What about if, instead of drawing $m_1$ and $m_2$ from a distribution randomly,
we required that their total mass equal $m_{12}$? Assume $m_1 \geq m_2$, then
\begin{align}
    P(q) &= \int\limits_{m_{\min}}^{m_{\max}}
            \int\limits_{m_{\min}}^{m_1}
            \delta\p{\frac{m_2}{m_1} - q}
            \delta\p{\frac{m_1 + m_2}{m_{12}} - 1}
            P(m_1)
            P\p{m_2}\;\mathrm{d}m_2\;\mathrm{d}m_1,\\
        &= \int\limits_{m_{\min}}^{m_{\max}}
            m_{12}\delta\p{\frac{m_{12} - m_1}{m_1} - q}
            P(m_1)
            P\p{m_{12} - m_1}\;\mathrm{d}m_1,\\
        &=\int\limits_{m_{\min}}^{m_{\max}}
            m_{12}
            \delta\p{\frac{m_{12}}{m_1} - (1 + q)}
            P\p{m_1}
            P\p{m_{12} - m_1}\;\mathrm{d}m_1,\\
        &= P\p{\frac{m_{12}}{1 + q}}P\p{m_{12} - \frac{m_{12}}{1 + q}}
            \p{\frac{m_{12}}{1 + q}}^2,\\
        &\propto \frac{q^{-p}}{\p{1 + q}^{-2p + 2}}.
\end{align}

\end{document}

